 

### 2023-04-26 markdown/methods.Rmd
flowchart updated

opts_box_setting <- gpar(fill="lightyellow", col="darkblue")
opts_txt_setting <- gpar(col="darkblue", cex=1)

# input files
evidence_file <- boxGrob({glue("evidence file",
                           .sep = "\n")})
sample_annotation_file <- boxGrob({glue("sample annotation",
                           .sep = "\n")})

@@

quality_control_2 <- boxGrob({glue("quality control 2",
                          .sep = "\n")})
qc2_content <- boxGrob(
                      "filter by reporter ion intensity cutoff\nfilter by pepitde covariance to razor protein\nremove peptides by missing rate",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

@@

transform_data <- boxGrob({glue("transform data",
                          .sep = "\n")})
transform_opts <- boxGrob(
                      "options:\nlog2\nlog10\nsqrt\nquadratic\nBoxCox\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

normalize_data <- boxGrob({glue("normalize data",
                          .sep = "\n")})
normalize_opts <- boxGrob(
                      "options:\nSCoPE2\nCONSTANd\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

missing_value_handling <- boxGrob({glue("missing value handling",
                          .sep = "\n")})
missing_value_opts <- boxGrob(
                      "options:\nKNN\ndrop rows\nreplace with mean\nreplace with median\nreplace with 0",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

batch_correction <- boxGrob({glue("batch correction",
                          .sep = "\n")})
batch_correction_opts <- boxGrob(
                      "options:\nComBat",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

dim_red <- boxGrob({glue("dimensionality reduction",
                          .sep = "\n")})
dim_red_actions <- boxGrob(
                      "procedures:\nPCA\nUMAP",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

@@

connectGrob(vert$quality_control_2, qc2_content, type = "horizontal", arrow_obj = arrow(angle=0))

connectGrob(vert$transform_data, transform_opts, type = "horizontal", arrow_obj = arrow(angle=0))

connectGrob(vert$normalize_data, normalize_opts, type = "horizontal", arrow_obj = arrow(angle=0))

connectGrob(vert$missing_value_handling, missing_value_opts, type = "horizontal", arrow_obj = arrow(angle=0))

connectGrob(vert$batch_correction, batch_correction_opts, type = "horizontal", arrow_obj = arrow(angle=0))

>>>>

opts_box_setting <- gpar(fill="lightyellow", col="darkblue")
opts_txt_setting <- gpar(col="darkblue", cex=1)
refinement_arrow_setting <- arrow(angle=30, ends="both", type = "closed")

plot_box_setting <- gpar(fill="#DDCC77")
# input files
evidence_file <- boxGrob({glue("evidence file",
                           .sep = "\n")})
sample_annotation_file <- boxGrob({glue("sample annotation",
                           .sep = "\n")})

@@

quality_control_2 <- boxGrob("quality control 2",
                             box_gp=plot_box_setting)
qc2_content <- boxGrob(
                      "filter by reporter ion intensity cutoff\nfilter by pepitde covariance to razor protein\nremove peptides by missing rate",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

@@

transform_data <- boxGrob("transform data",
                          box_gp=plot_box_setting)
transform_opts <- boxGrob(
                      "options:\nlog2\nlog10\nsqrt\nquadratic\nBoxCox\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

normalize_data <- boxGrob("normalize data",
                          box_gp=plot_box_setting)
normalize_opts <- boxGrob(
                      "options:\nSCoPE2\nCONSTANd\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

missing_value_handling <- boxGrob("missing value handling",
                                  box_gp=plot_box_setting)
missing_value_opts <- boxGrob(
                      "options:\nKNN\ndrop rows\nreplace with mean\nreplace with median\nreplace with 0",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

batch_correction <- boxGrob("batch correction",
                            box_gp=plot_box_setting)
batch_correction_opts <- boxGrob(
                      "options:\nComBat",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

dim_red <- boxGrob("dimensionality reduction",
                   box_gp=plot_box_setting)
dim_red_actions <- boxGrob(
                      "procedures:\nPCA\nUMAP",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

@@

connectGrob(vert$quality_control_2, qc2_content, type = "horizontal", arrow_obj = refinement_arrow_setting)

connectGrob(vert$transform_data, transform_opts, type = "horizontal", arrow_obj = refinement_arrow_setting)

connectGrob(vert$normalize_data, normalize_opts, type = "horizontal", arrow_obj = refinement_arrow_setting)

connectGrob(vert$missing_value_handling, missing_value_opts, type = "horizontal", arrow_obj = refinement_arrow_setting)

connectGrob(vert$batch_correction, batch_correction_opts, type = "horizontal", arrow_obj = refinement_arrow_setting)
